Type-Safe Client-Server Communication in Web Applications

### 2014-02-27 paper.tex
Add checklist for implementation section.

In order to make an RPC call using a handle obtained from \lstinline!export!,
we must supply it with an argument. This is done using the \lstinline!<.>!
operator. Upon closer inspection, the attentive reader may notice that
\linebreak
its type, \lstinline!Serialize a => Export (a -> b) -> a -> Export b!,
is very similar to the type of the \lstinline!<*>! operator over applicative
functors. This is not a coincidence; the \lstinline!<.>! performs the same role
for the \lstinline!Export! type as \lstinline!<*>! performs for applicative
functors. The reason for using a separate operator for this instead of making
\lstinline!Export! an instance of \lstinline!Applicative! is that since
functions embedded in the \lstinline!Export! type exist only to be called over
a network, such functions must only be applied to arguments which can be
serialized and sent over a network connection.

@@

\section{Implementation}
\section{The Haste compiler}

>>>>

In order to make an RPC call using a handle obtained from \lstinline!export!,
we must supply it with an argument. This is done using the \lstinline!<.>!
operator. Upon closer inspection, the attentive reader may notice that
\linebreak
its type, \lstinline!Serialize a => Export (a -> b) -> a -> Export b!,
is very similar to the type of the \lstinline!<*>! operator over applicative
functors. This is not a coincidence; the \lstinline!<.>! performs the same role
for the \lstinline!Export! type as \lstinline!<*>! performs for applicative
functors. The reason for using a separate operator for this instead of making
\lstinline!Export! an instance of \lstinline!Applicative! is that since
functions embedded in the \lstinline!Export! type exist only to be called over
a network, such functions must only be applied to arguments which can be
serialized and sent over a network connection. When an \lstinline!Export!
function is applied to an argument using \lstinline!<.>!, the argument is
serialized and stored inside the resulting \lstinline!Export! object, awaiting
dispatch.

@@

\subsection{The chatbox, revisited}

\section{Implementation}

\begin{itemize}
  \item Poor man's concurrency monad
  \item Conditional compilation
  \item Printf trick to turn export into [JSON] -> f
  \item JSON over WebSockets used for transport
  \item Server event loop awaits commands, dispatches functions, sends data back
  \item Client sends command with nonce and blocks on MVar, event loop fills
        MVar when return value with proper nonce arrives
  \item Throw away unused stuff on client
\end{itemize}

\section{The Haste compiler}
